---
title: "Statistical_analysis_Pei"
author: "Pei Liu"
date: "2022-11-29"
output: html_document
---


```{r}
library(viridis)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
```


```{r}
library(tidyverse)
library(ggridges)
library(dplyr)
raw_data<-read_csv(file="./data/DOHMH_Childcare_Center_Inspections .csv")
```


# Part I: data cleaning 

filter the variables to include currently permitted Children Care Center
Question: should we consider permitted (17356) or permitted+ active (3399)(school)

step1:filter the inspection record for only currently permitted Children Care Center
step2:remove the useless variables: legal_name, building, street, phone, permit_number, permid_expiration, day care id, url, date_permitted, actual.
(some of them might be helpful in plotly percedure)

```{r}
Childcare_center<-
  raw_data%>%
  janitor::clean_names() %>%
  filter(status=="Permitted")%>%
  select(-legal_name,-building,-street,-phone,-permit_number,-permit_expiration,
         -day_care_id,-url,-date_permitted,-actual)%>%
  drop_na(violation_rate_percent)%>% ## change from 17356 to 15910
  drop_na(public_health_hazard_violation_rate) %>% ## actually no change
  filter(age_range != "0 YEARS - 16 YEARS")
Childcare_center
```




Frequency of Violation Category for Each center
```{r}
Childcare_center %>% 
  group_by(violation_category, center_name) %>% 
  summarise(count = n()) %>% 
  knitr::kable()
```
There are 1197 permitted center in NYC now.
```{r}
length(unique(Childcare_center$center_name))
```

The relationship between Violation Category and Maximum capacity:
```{r}
Childcare_center %>% 
  group_by(violation_category, maximum_capacity) %>% 
  #summarise(count = n(), mean = mean()) %>% 
  ggplot(aes(x = violation_category, y = maximum_capacity)) +
  geom_violin(aes(fill = violation_category), 
              color = "blue", 
              alpha = .5) +
  theme(legend.position = "bottom") 

Childcare_center %>% 
  group_by(violation_category, maximum_capacity) %>% 
  #summarise(count = n(), mean = mean()) %>% 
  ggplot(aes(x = violation_category, y = maximum_capacity, color = violation_category)) +
  geom_boxplot() +
  theme(legend.position = "bottom") 
```
```{r}

Childcare_center %>% 
  group_by(violation_category, total_educational_workers) %>% 
  #summarise(count = n(), mean = mean()) %>% 
  ggplot(aes(x = violation_category, y = total_educational_workers)) +
  geom_violin(aes(fill = violation_category), 
              color = "blue", 
              alpha = .5) +
  theme(legend.position = "bottom") 

Childcare_center %>% 
  group_by(violation_category, total_educational_workers) %>% 
  #summarise(count = n(), mean = mean()) %>% 
  ggplot(aes(x = violation_category, y = total_educational_workers, color = violation_category)) +
  geom_boxplot() +
  theme(legend.position = "bottom") 

```
```



Top 10 regulation summaries in NYC
```{r}
Childcare_center %>% 
  group_by(regulation_summary) %>% 
  summarise(number = n()) %>% 
  arrange(desc(number)) %>% 
  top_n(11)
```







```{r}
Childcare_center %>% 
  ggplot(aes(x = total_educational_workers, y = violation_rate_percent)) +
  geom_point()
```



1. Overview of Childcare Center in NYC
1.1 Frequency of Child care center by borough
1.2 Frequency of Program Type (Age range) for the whole city and by borough
1.3 Total educational workers and Maximum Capacity (average worker per child) in NYC and by borough

2. Violation Analysis
2.1 Borough versus violation category
2.2 Top 10 regulation summary in each borough
2.3 Program type vs violation category

Kristin: Borough
Wenjun: AGe group
Emma: Top 10 regulation summary in each borough, Total educational workers and Maximum Capacity
Keming: Program Type 