---
title: "statistical_analysis"
author: "Shuting Kang"
date: "2022-11-27"
output: html_document
---

This markdown file is use for project statistical analysis 

step1: input dataset DOHMH Childcare Center Inspections (Updated from november 25,2022) from NYC OpenData 
```{r }
library(tidyverse)
library(ggridges)
raw_data<-read_csv(file="./data/DOHMH_Childcare_Center_Inspections .csv")
```

# Part I: data cleaning 

filter the variables to include currently permitted Children Care Center
Question: should we consider permitted (17356) or permitted+ active (3399)(school)

step1:filter the inspection record for only currently permitted Children Care Center
step2:remove the useless variables: legal_name, building, street, phone, permit_number, permid_expiration, day care id, url, date_permitted, actual.
(some of them might be helpful in plotly percedure)

```{r}
Childcare_center<-
  raw_data%>%
  janitor::clean_names() %>%
  filter(status=="Permitted")%>%
  select(-legal_name,-building,-street,-phone,-permit_number,-permit_expiration,
         -day_care_id,-url,-date_permitted,-actual)%>%
  drop_na(violation_rate_percent)%>% ## change from 17356 to 15910
  drop_na(public_health_hazard_violation_rate)## actually no change
Childcare_center
```


```{r}
skimr::skim(Childcare_center)
```
categorical variables: 
center name: 1306 we can divided into five parts based on their borough 
borough: 5
age range:3
program type: 4
facility type:2
child care type:3
violation category: 3
health code sub section:264???
## violation status: 3
inspection summary result: 28

numerical variables:
maximum capacity
total education workers
## violation rate percent
## public health hazard violation rate
## critical violation rate

target variables:
violation rate percent (numerical)
public health hazard violation rate (numerical)
critical violation rate (numerical)
violation status (categorical) 

! Attention:
Average Violation rate percent: based on child care type (only three values)
Average Total Educational Workers: based on the program type (only four values)
Average Public Health Hazard Violation Rate: based on child care type (only three values)
Average Critical Violation Rate: based on child care type (only three values)

So, we should not use these averaged value...

# Part II: EDA
## Bivariate visualization 

1. borough(5) 
1.1 plots
1.1.1 borough versus violation rate percent & public health hazard violation rate & critical violation rate
```{r}
plot_1.1.1_1<-
  Childcare_center%>%
  group_by(borough)%>%
  select(borough,violation_rate_percent,public_health_hazard_violation_rate,critical_violation_rate)%>%
  pivot_longer(
    violation_rate_percent:critical_violation_rate,
    names_to="observation",
    values_to = "value"
  )%>%
  ggplot(aes(x=borough,y=value,color=observation))+
  geom_boxplot()
plot_1.1.1_1  
```
```{r}
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

plot_1.1.1_violin<-
  Childcare_center%>%
  group_by(borough)%>%
  select(borough,violation_rate_percent)%>%
  ggplot(aes(x=borough,y=violation_rate_percent))+
  geom_violin(aes(fill = borough), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom")
plot_1.1.1_violin 

plot_1.1.1_boxplot<-
  Childcare_center%>%
  group_by(borough)%>%
  select(borough,violation_rate_percent)%>%
  ggplot(aes(x=borough,y=violation_rate_percent))+
  geom_boxplot(aes(fill = borough), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom")
plot_1.1.1_boxplot


plot_1.1.1_violin2<-
  Childcare_center%>%
  group_by(borough)%>%
  select(borough,public_health_hazard_violation_rate)%>%
  ggplot(aes(x=borough,y=public_health_hazard_violation_rate))+
  geom_violin(aes(fill = borough), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom")
plot_1.1.1_violin2

plot_1.1.1_boxplot2<-
  Childcare_center%>%
  group_by(borough)%>%
  select(borough,public_health_hazard_violation_rate)%>%
  ggplot(aes(x=borough,y=public_health_hazard_violation_rate))+
  geom_boxplot(aes(fill = borough), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom")
plot_1.1.1_boxplot2

plot_1.1.1_violin3<-
  Childcare_center%>%
  group_by(borough)%>%
  select(borough,critical_violation_rate)%>%
  ggplot(aes(x=borough,y=critical_violation_rate))+
  geom_violin(aes(fill = borough), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom")
plot_1.1.1_violin3

plot_1.1.1_boxplot3<-
  Childcare_center%>%
  group_by(borough)%>%
  select(borough,critical_violation_rate)%>%
  ggplot(aes(x=borough,y=critical_violation_rate))+
  geom_boxplot(aes(fill = borough), color = "blue", alpha = .5) + 
  theme(legend.position = "bottom")
plot_1.1.1_boxplot3

```

```{r}
library(patchwork)
(plot_1.1.1_violin+plot_1.1.1_violin2+plot_1.1.1_violin3)/(plot_1.1.1_boxplot+plot_1.1.1_boxplot2+plot_1.1.1_boxplot3)
```

```

```{r}

plot_1.1.1<-
  Childcare_center%>%
  group_by(borough)%>%
  summarise(ave_vrp=mean(violation_rate_percent),
         ave_phhvr=mean(public_health_hazard_violation_rate),
         ave_cvr=mean(critical_violation_rate))%>%
  pivot_longer(
    ave_vrp:ave_cvr,
    names_to="observation",
    values_to = "value"
  )%>%
  ggplot(aes(x=borough,y=value,color=observation))+
  geom_point()
plot_1.1.1
```
1.1.2 borough versus violation status 


1.2 analysis output
The target output will significantly influenced by borough




age range:3
program type: 4
facility type:2
child care type:3
violation category: 3
health code sub section:264
inspection summary result: 28
```{r}

```
